*Supplement* Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-12-15 supplement.qmd
S prefix to manual tables in supp

Summary of mixed-effects models evaluating increases in the number of days each year from 1975 to 2022 when temperature or salinity were above or below critical thresholds, respectively. The slope estimates in the "Both" column indicate trends in the number of days when both temperature and salinity were above or below critical thresholds. \*\* p \< 0.005, \* p \< 0.05, - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Summary of mixed-effects models evaluating increases in the number of days each year from 1998 to 2022 when temperature or salinity were above or below critical thresholds, respectively. The slope estimates in the "Both" column indicate trends in the number of days when both temperature and salinity were above or below critical thresholds. \*\* p \< 0.005, \* p \< 0.05, - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Number of days at the beginning and end of the period of record when temperature or salinity were above or below critical thresholds, respectively. Values are the estimated mean number of days (plus standard error) from 1975 to 2022. Columns for "Both" indicate the estimated number of days when both temperature and salinity were above or below critical thresholds. Note that not all models are significant (see table 3). - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Number of days at the beginning and end of the period of record when temperature or salinity were above or below critical thresholds, respectively. Values are the estimated mean number of days (plus standard error) from 1998 to 2022. Columns for "Both" indicate the estimated number of days when both temperature and salinity were above or below critical thresholds. Note that not all models are significant (see table 4). - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

>>>>

Table S3: Summary of mixed-effects models evaluating increases in the number of days each year from 1975 to 2022 when temperature or salinity were above or below critical thresholds, respectively. The slope estimates in the "Both" column indicate trends in the number of days when both temperature and salinity were above or below critical thresholds. \*\* p \< 0.005, \* p \< 0.05, - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Table S4: Summary of mixed-effects models evaluating increases in the number of days each year from 1998 to 2022 when temperature or salinity were above or below critical thresholds, respectively. The slope estimates in the "Both" column indicate trends in the number of days when both temperature and salinity were above or below critical thresholds. \*\* p \< 0.005, \* p \< 0.05, - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Table S5: Number of days at the beginning and end of the period of record when temperature or salinity were above or below critical thresholds, respectively. Values are the estimated mean number of days (plus standard error) from 1975 to 2022. Columns for "Both" indicate the estimated number of days when both temperature and salinity were above or below critical thresholds. Note that not all models are significant (see table 3). - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

@@

Table S6: Number of days at the beginning and end of the period of record when temperature or salinity were above or below critical thresholds, respectively. Values are the estimated mean number of days (plus standard error) from 1998 to 2022. Columns for "Both" indicate the estimated number of days when both temperature and salinity were above or below critical thresholds. Note that not all models are significant (see table 4). - no model. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.
